%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Certifications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	% -------------------------------------------
	\cventry
	{SQL for Data Analytics} % Certification Title
	{Udemy} % Organization
	{\textcolor{neutraltext}{Oct 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Acquired advanced SQL skills tailored for data analytics, enabling the extraction and manipulation of large datasets.
			\item Worked with PostgreSQL to execute complex queries, join tables, and aggregate data for in-depth analysis.
			\item Gained expertise in database management, optimizing queries, and enhancing data processing efficiency.
			\item Developed the ability to create and manage databases, handle data cleaning, and prepare data for analysis and reporting.
		\end{cvitems}
	}
	
	
	% -------------------------------------------
	
	\cventry
	{Hypothesis Testing in Python} % Certification Title
	{DataCamp} % Organization
	{\textcolor{neutraltext}{Sep 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Gained hands-on experience in conducting hypothesis tests using Python to draw statistically rigorous conclusions from datasets.
			\item Learned when and how to apply common hypothesis tests such as t-tests, chi-square tests, and proportion tests to analyze data.
			\item Worked with real-world datasets, including Stack Overflow user feedback and supply chain data, to test hypotheses and validate assumptions.
			\item Explored non-parametric tests to extend beyond the limitations of traditional tests, improving the accuracy of statistical analysis.
		\end{cvitems}
	}
	
	% -------------------------------------------
	
	\cventry
	{Data Analysis with Pandas} % Certification Title
	{Udemy} % Organization
	{\textcolor{neutraltext}{Aug 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Gained proficiency in using Pandas for data manipulation, cleaning, and transformation.
			\item Learned how to efficiently handle and analyze large datasets, perform aggregations, and merge datasets.
			\item Applied advanced Pandas techniques to extract insights, perform exploratory data analysis (EDA), and prepare data for machine learning tasks.
			\item Developed skills in handling time-series data, and applying groupby operations for in-depth analysis.
		\end{cvitems}
	}
	
	% -------------------------------------------
	\cventry
	{Python for OOP} % Certification Title
	{Udemy} % Organization
	{\textcolor{neutraltext}{Aug 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Mastered the concepts of Object-Oriented Programming (OOP) in Python, including classes, objects, inheritance, and polymorphism.
			\item Learned how to design and implement reusable, modular code through classes and methods.
			\item Developed a deep understanding of object-oriented design patterns and how to apply them in Python projects.
			\item Enhanced problem-solving skills by applying OOP principles to real-world programming challenges.
		\end{cvitems}
	}
	 
	% -------------------------------------------
	
	\cventry
	{Sampling in Python} % Certification Title
	{DataCamp} % Organization
	{\textcolor{neutraltext}{Aug 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Gained expertise in sampling techniques, including simple random sampling, stratified sampling, and cluster sampling for statistical analysis.
			\item Learned how to estimate population parameters and quantify uncertainty using sampling distributions and bootstrap distributions.
			\item Applied sampling methods to real-world datasets such as coffee ratings, Spotify songs, and employee attrition for inference and analysis.
			\item Developed a solid understanding of the principles behind survey analysis and experimental design in Python.
		\end{cvitems}
	}
	
	% -------------------------------------------
	
	\cventry
	{Statistical Thinking in Python} % Certification Title
	{DataCamp} % Organization
	{\textcolor{neutraltext}{Aug 2024}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Developed a foundational understanding of statistical inference, a crucial step in the data analysis pipeline.
			\item Learned how to draw clear, data-driven conclusions by applying statistical thinking and using Python-based tools.
			\item Gained the ability to interpret data, speak the language of statistics, and communicate insights effectively.
			\item Built a strong statistical thinking foundation, accelerating the ability to analyze data and derive insights with speed and precision.
		\end{cvitems}
	}
	
	% -------------------------------------------
	
	\cventry
	{Intermediate PostgreSQL} % Certification Title
	{Coursera} % Organization
	{\textcolor{neutraltext}{Nov 2023}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Gained proficiency in advanced PostgreSQL techniques, including complex queries, performance tuning, and optimization.
			\item Learned how to work with advanced data types, window functions, and subqueries to extract insights from large datasets.
			\item Enhanced database management skills with hands-on experience in database schema design, indexing, and SQL query optimization.
		\end{cvitems}
	}
	
	% -------------------------------------------
		
	\cventry
	{Task-Oriented Course in SQL} % Certification Title
	{Quera} % Organization
	{\textcolor{neutraltext}{Sep 2023}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Mastered SQL through a hands-on, task-oriented approach, focusing on solving real-world problems with SQL queries.
			\item Developed expertise in data manipulation, aggregation, and complex joins to retrieve and analyze information efficiently.
			\item Acquired skills in database design and performance optimization, enabling more effective database management.
		\end{cvitems}
	}
		% -------------------------------------------
	
	\cventry
	{Advanced AI with TensorFlow and Keras} % Certification Title
	{Utech Academy} % Organization
	{\textcolor{neutraltext}{Dec 2021}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Explored advanced concepts of artificial intelligence, focusing on deep learning techniques using TensorFlow and Keras.
			\item Implemented and fine-tuned complex neural network architectures, including Convolutional Neural Networks (CNNs), and Generative Adversarial Networks (GANs).
			\item Learned techniques for optimizing model performance, such as hyperparameter tuning, regularization, and data augmentation..
		\end{cvitems}
	}
	
	% -------------------------------------------
	
	\cventry
	{Using Python to Interact with the Operating System} % Certification Title
	{Coursera} % Organization
	{\textcolor{neutraltext}{May 2021}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Gained practical knowledge of interacting with the operating system using Python, including file manipulation and process management.
			\item Learned to automate tasks such as file system navigation, batch processing, and system administration tasks using Python scripts.
			\item Developed skills in leveraging Python's `os` and `shutil` modules to perform operating system-related tasks more efficiently.
		\end{cvitems}
	}
	% -------------------------------------------
	
	\cventry
	{Machine Learning} % Certification Title
	{Coursera} % Organization
	{\textcolor{neutraltext}{Aug 2020}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Acquired foundational knowledge in machine learning, covering algorithms such as linear regression, logistic regression, and decision trees.
			\item Gained practical experience in training and evaluating models, as well as understanding the underlying principles of supervised and unsupervised learning.
			\item Developed proficiency in using machine learning libraries such as scikit-learn for building and optimizing predictive models.
		\end{cvitems}
	}
	
	% -------------------------------------------
	
	\cventry
	{Data Science Winter School} % Certification Title
	{Tehran Institute for Advanced Studies (TeIAS)} % Organization
	{\textcolor{neutraltext}{Feb 2020}} % Date
	{} % Location
	{
		\begin{cvitems} % Description
			\item Participated in an intensive Data Science Winter School, gaining hands-on experience in data analysis, machine learning, and data visualization.
			\item Collaborated on projects that involved statistical analysis, feature engineering, and model evaluation using Python and R.
			\item Engaged in practical workshops covering a range of topics, including data wrangling, predictive modeling, and visualization with tools like Pandas, Matplotlib, and Seaborn.
		\end{cvitems}
	}
	
	
\end{cventries}
