%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{Teaching Assistant} % Job title
	{Pars University of Art \& Architecture} % Organization
	{Tehran, Iran} % Location
	{\textcolor{neutraltext}{Sep 2024 --- Present}} % Date(s)
	{
		\begin{cvitems}
			\item Assisted students in developing design concepts based on the principle of balance, utilizing Python and Grasshopper within the Rhino environment. 
			\item Provided guidance on algorithmic design techniques and supported the integration of computational tools in the creative process.
		\end{cvitems}
	}
	%---------------------------------------------------------
	\cventry
	{Data Analysis Intern} % Job title
	{Quera} % Organization
	{Tehran, Iran} % Location
	{\textcolor{neutraltext}{Apr 2023 --- Jul 2023}} % Date(s)
	{
		\begin{cvitems}
			\item Utilized Pandas, Numpy, and Matplotlib for data manipulation 
			\item Engineered a robust web scraping solution using BeautifulSoup and Selenium, extracting over 200,000 data points from competitor websites; insights directly informed pricing strategies and improved market positioning by identifying gaps.
			\item Created an intuitive interface through a custom-built web application on the Streamlit framework; provided insights leading to actionable recommendations addressing two major project bottlenecks identified by teams.
			\item Implemented and managed a SQL database with SQLAlchemy
			\item Employed scikit-learn for predictive modeling and classification
			\item Gained experience in using PowerBI for data analytics.
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Teaching Assistant} % Job title
	{University of Tehran} % Organization
	{Tehran, Iran} % Location
	{\textcolor{neutraltext}{Jan 2024 --- Jul 2024}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Assisted students in creating algorithmic designs using Python and Grasshopper, focusing on the development of complex geometries for 3D printing.
			\item Provided guidance on the integration of computational design techniques, helping students refine their design processes and prepare models for fabrication.
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{AI Developer} % Job title
	{Shenasa-AI} % Organization
	{Tehran, Iran} % Location
	{\textcolor{neutraltext}{Dec 2020 --- Sep 2021}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Engineered advanced AI algorithms to diagnose COVID-19 and pneumonia, achieving a diagnostic accuracy rate of 95\% through the analysis of over 10,000 CT scan datasets.
			\item Utilized machine learning frameworks such as Keras and TensorFlow to build deep learning models for accurate medical image analysis.
			\item Applied computer vision techniques to detect and classify abnormalities in CT scans, contributing to healthcare applications.
		\end{cvitems}
	}
	
\end{cventries}
