%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{M.Sc. Thesis} % Role
	{Generating 2D Urban Networks in Tehran via GAN and DL} % Event
	{} % Location
	{} % Date(s)
	{
		\begin{cvitems} % Description(s)
			\item{Focused on generating 2D urban networks for Tehran using advanced techniques in deep learning (DL), Generative Adversarial Networks (GAN), and image segmentation.}
			\item{Developed neural network models to create synthetic urban network images, contributing to urban design and planning research.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Self-initiated Project} % Role
	{Scraping TransferMarkt and Extracting Insights (\href{https://github.com/mohammedbehjoo/transfermark_scrapy}{GitHub})} % Event
	{} % Location
	{\textcolor{neutraltext}{2024}} % Date(s)
	{
		\begin{cvitems} % Description(s)
			\item{Scraped detailed data on football leagues, teams, and players from Transfermarkt using the Scrapy package.}
			\item{Organized and stored the extracted data in a structured format for analysis and further processing.}
			\item Processed and structured large volumes of data into clean, \item usable formats for analysis, including JSON and CSV files.
			Conducted exploratory data analysis (EDA) and statistical analysis to identify trends, team performance metrics, and player statistics.
			\item{Developed interactive visualizations to present the findings, aiding in better understanding and decision-making.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------

		
		%---------------------------------------------------------
		\cventry
		{Self-initiated Project} % Role
		{Human Development Reports (HDR) Dataset Analysis (\href{https://github.com/mohammedbehjoo/UN_HDR_data_analysis}{GitHub})} % Event
		{} % Location
		{\textcolor{neutraltext}{2024}} % Date(s)
		{
			\begin{cvitems} % Description(s)
				\item{Conducted exploratory data analysis (EDA) and statistical analysis on the Human Development Reports (HDR) dataset sourced from the UNDP Data Center.}
				\item{Gained insights into global human development metrics, focusing on factors such as education, life expectancy, and income.}
				\item{Developed an interactive multipage Streamlit app to visualize the data, allowing users to explore key trends and metrics.}
			\end{cvitems}
		}
	
	%---------------------------------------------------------
	
\end{cventries}
